\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
reviewing correcting and uploading

Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields. Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon\red{(SENTENCE SEEMS INCOMPLETE ... WHAT WERE THE CONTRIBUTION OF THESE AUTHORS ???)}.

\medskip
In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap. The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) \red{(THIS SENTENCE IS A BIT CONFUSING ... SO THE EQNS THAT DESCRIBE FLOWS IN H-S CELLS ARE THE POTENTIAL EQUATION FOR INVISCID FLUIDS AND THE DARCY EQN? ... TRY TO REWRITE THE SENTENCE AND EXPLAIN THE IMPORTANCE OF THE H-S CELLS IN THE UNDERSTANDING OF VISCOUS FLOW INSTABILITIES)}. More recently, \citet{howison_2000} and \citet{praud_2005} gave an extensive \red{(DO YOU MEAN EXTENSIVE OR COMPREHENSIVE?)} description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).

\medskip
 Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}. During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{buckley_1942,sheldon_1959} leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'. In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface. The interface becomes unstable and collapses, taking a curved shape.

>>>>

Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields. \citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number as this is defined below in eq.\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
T is the surface tension and U is a velocity characteristic of the moving interface.

\begin{equation}
Ca = \frac{\mu U}{T}
\label{eq:capillary_number}
\end{equation}

For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number. If \textit{Ca} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and other agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity U.

\medskip
In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap. The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) \red{(THIS SENTENCE IS A BIT CONFUSING ... SO THE EQNS THAT DESCRIBE FLOWS IN H-S CELLS ARE THE POTENTIAL EQUATION FOR INVISCID FLUIDS AND THE DARCY EQN? ... TRY TO REWRITE THE SENTENCE AND EXPLAIN THE IMPORTANCE OF THE H-S CELLS IN THE UNDERSTANDING OF VISCOUS FLOW INSTABILITIES)}. More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).

\medskip
 Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}. During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed %\citep{(described by the Buckley-Leverett theory of immiscible displacement){buckley_1942,sheldon_1959}} 
leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'. In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface. The interface becomes unstable and collapses, taking a curved shape.
